---
title: "FA4"
author: "Espiritu, Empeno"
date: "`r Sys.Date()`"
output: 
  github_document: default
  html_document: default
  pdf_document: default
---

```` {r echo = FALSE}
library(moments)
library(DescTools)
````

### **FA6 Questions**

#### ***1.*** A geospatial analysis system has four sensors supplying images. The percent- age of images supplied by each sensor and the percentage of images relevant to a query are shown in the following table.

```` {r echo = FALSE}
# Create the data frame
sensor_data <- data.frame(
  Sensor = c(1, 2, 3, 4),
  `Percentage_of_Images_Supplied` = c(15, 20, 25, 40),
  `Percentage_of_Relevant_Images` = c(50, 60, 80, 85)
)

# Print the table
knitr::kable(sensor_data, format = "markdown")
````

What is the overall Percentage of the Relevant Images?

```{r}
percentSupplied <- c(15, 20, 25, 40)
percentRelevant <- c(50, 60, 80, 85)

overallPercentage <- sum(percentSupplied * percentRelevant) / sum(percentSupplied)

cat("Overall percentage of the Relevant images:", overallPercentage, "%\n")
```
#### ***2.*** A fair coin is tossed twice.
Let E be the event that both tosses have the same outcome, that is, E1 = (HH, TT).
Let E2 be the event that the first toss is a head, that is, E2 = (HH, HT).
Let E3 be the event that the second toss is a head, that is, E3 = (TH, HH).
Show that E1, E2, and E3 are pairwise independent but not mutually independent.

```` {r echo = FALSE}
coinToss <- matrix(c("HH", "TH", "HT", "TT"), nrow = 2, ncol = 2)
rownames(coinToss) <- c("Heads", "Tails")
colnames(coinToss) <- c("Heads", "Tails")


knitr::kable(coinToss, format = "markdown")


E1 <- c("HH","TT")
E2 <- c("HH","HT")
E3 <- c("TH","HH")

cat("E1 is the Event both results are the Same")
cat("E2 is the Event first results are the Heads")
cat("E1 is the Event second results are the Heads")

prob_E1 <- 1/2
prob_E2 <- 1/2
prob_E3 <- 1/2

cat("From the table we can see each event has 1/2 of the chance")
cat(prob_E1, prob_E2, prob_E3)

cat("The two events E1 UNION E2 happening are the the products of its probabilities")

cat(prob_E1*prob_E2, "Which is just the probability of HH on the table which is 1/4 and the UNION of the two events is HH")

cat("We can derive that E1 UNION E3 and E2 UNION E3 will also have 1/4 probabilities\nand respectively have HH as the UNION too")

cat(prob_E1*prob_E3, prob_E2*prob_E3)

cat("These prove their Pairwise Independent but now to show they are not Mutually Independent.\nWe can just apply the same priciple of multiplying the Probabilities and theirs UNION's and we will see the probem")

cat("E1 UNION E2 UNION E3 have HH as the probability which is 1/4 but is not equal to the probability of multiplying all of them")

cat(prob_E1*prob_E2*prob_E3, "Hence they are not Mutually Independent because E2 and E3 itself doesnt cary information or\ndata to help form the probability of E1 it is still 1/2 but having the UNION of E2 and E2 will\nchange the probability of E1 to happen becoming 1 means its guaranteed")
````


















